Dark matter halo concentrations with a bayesian approach

### 2014-05-27 paper/article.tex
removed comma

The method we use to generate the halos is based on the integrated
mass profile. Given the number of particles $n$ and the concentration $c$ we define the mass element as $\delta m = 1/n$ (this corresponds to the mass of each particle, such that the total mass is one). Then for each number $k$ from $1$ to $n$ we find the value of $r$ such that
\begin{equation}
m(<r;c)-k \cdot \delta m 
\end{equation}
is zero using Ridders' method. This value of $r$ will be the radius of the $k$th particle of the generated halo, then polar and azimuthal angles $\theta$ and $\phi$ are generated randomly. Finally these three coordinates are transformed into cartesian coordinates $(r,\theta,\phi) \rightarrow (x,y,z)$. This process is repeated $n$ times in order to generate the $x,y,z$ coordinates for each particle.

>>>>

The method we use to generate the halos is based on the integrated
mass profile. Given the number of particles $n$ and the concentration $c$ we define the mass element as $\delta m = 1/n$ (this corresponds to the mass of each particle such that the total mass is one). Then for each number $k$ from $1$ to $n$ we find the value of $r$ such that
\begin{equation}
m(<r;c)-k \cdot \delta m 
\end{equation}
is zero using Ridders' method. This value of $r$ will be the radius of the $k$th particle of the generated halo, then polar and azimuthal angles $\theta$ and $\phi$ are generated randomly. Finally these three coordinates are transformed into cartesian coordinates $(r,\theta,\phi) \rightarrow (x,y,z)$. This process is repeated $n$ times in order to generate the $x,y,z$ coordinates for each particle.
